Multi-Objective Optimization in Image Approximation \\ {} \thanks{The publication has been prepared with the support of Velbazhd Software LLC and Bulgarian Ministry of Education and Science according to the research project No. {D01–205/23.11.2018}.}

### 2020-09-04 Multiobjective-Optimization-in-Image-Approximation/paper.tex
Small fixes were done.

@@

Six separate experiments were executed. As it is shown in Fig. \ref{fig02}-\ref{fig07}, the most informative elements of the bitmap image are kept in the approximated images. There are some deviations in the results, but it is expected because of the probabilistic nature of the genetic algorithms. The count of the ellipses used for the approximation is relatively acceptable, but the presence of obvious blank areas is not of the desired amount.

@@

In this paper, multi-objective optimization was proposed for image approximation. As an optimization tool, genetic algorithms are used. The experimental results clearly show that approximated images are pretty accurate with the limitation of color reduction and vectorization. The convergence of the optimization process is very related to the probabilistic nature of the genetic algorithms. Because of this, the implementation of an efficient fitness function is critical in the process. The main disadvantage of the proposed solution is the time-consuming raster image cooperation.

>>>>

A precise formulation of the problem is available in the public domain \cite{Balabanov-2020}. A precise description of the used genetic algorithm is available at \cite{Apache-Commons-Command-Line-Interface-2020}.

@@

Six separate experiments were executed. As it is shown in Fig. \ref{fig02}-\ref{fig07}, the most informative elements of the bitmap image are kept in the approximated images. There are some deviations in the results, but it is expected because of the probabilistic nature of the genetic algorithms. The number of the ellipses used for the approximation is acceptable (if the number is too high it will be time and paint consuming), but the presence of obvious blank areas is not of the desired amount. Each interested reader can try different genetic algorithm parameters with different images of his/her own choice, because of the implemented command-line interface.

@@

In this paper, multi-objective optimization was proposed for image approximation. As an optimization tool, genetic algorithms are used. The experimental results clearly show that approximated images are perception close with the limitation of color reduction and vectorization. The convergence of the optimization process is very related to the probabilistic nature of the genetic algorithms. Because of this, the implementation of an efficient fitness function is critical in the process. The main disadvantage of the proposed solution is the time-consuming raster image cooperation.
